Calculating life expectancy and exploring missingness

### 2016-10-28 Code/1_Explore_Data_v2.Rmd

```{r calculate_cod_decomp}
#takes about 20 mins
list.cod.decomp.tables <- vector(mode = "list", length = dim(paired.ids)[1])

>>>>

```{r calculate_cod_decomp}
#stopped here - need to figure this out
#if the count of deaths == 0 for all causes of death within an age band then the COD proportion is NA
#this messes up the cod decomposition. What to do?
#example - no black people dying between the ages of 5-9 of anything. but have whites dying in that age group so their
#COD proportions are okay.

#takes about 20 mins
list.cod.decomp.tables <- vector(mode = "list", length = dim(paired.ids)[1])
